Capon Beamforming and Moving Objects - An Analysis of Lateral Shift-Invariance

### 2014-02-18 HRUIofMovingObjects/response_to_reviewers.tex

As my scores indicate, I think the paper addresses an interesting problem and does it very well. Beside two VERY minor typos, I think it can be published unaltered.
1. "In" missing at the beginning of the Introduction section.
2. In section IIB, the opening sentence, there is an 's' missing in 'produce'.

\textit{We want to thank the reviewer for an encouraging review. Typos have been corrected.}

\section*{Reviewer: 2}

Thanks to the authors for addressing the problem of the temporal aspects in minimum variance beamforming, demonstrating the extra requirements on spatial sampling, and demonstrating how to efficiently oversample. The paper is good but I would like it to go through a second review round based on the following comments:
\textit{We want to thank the reviewer for an encouraging review. Below follows our response to his/her comments.}
\\\\
Page2 column2 lines 34-35, and Fig. 1, L, M and d have not been introduced (need to have read the previous literature or equation (4) to know their meaning). I would suggest that in the introduction we do not need these details.
\textit{(Should we remove this?)}
\\\\
Equation (8) the two factors p and q are confusing. Because q is always one, I would suggest omitting it.  Let us say that the oversampling is used both for Capon and for reducing folding of frequencies over the bandwidth.
\textit{We do not find this confusing, $p$ is always 2 and $q$ is 4 and 16 when oversampling on transmit is applied for the Capon beamformer.}
\\\\
At what depth are the LSV plots taken with respect to the focal depth? Does it matter?
\textit{The shift-invariance caused by under-sampling will be at its maximum at the transmit focus. Simulated LSV-plots are generated from this point, as specified on page 5, first paragraph.}
\\\\
Please specify the characteristics of the M5S probe (size, number of elements) if GE permits. Is it a phased or a linear array? What is the physical beam spacing, the field of view, the number of transmit and receive beams in the base (non oversampled) configuration? What is the transmit focal depth? Are transmit and receive apodization applied? Without this information, the work is not reproductible.
\textit{More extensive information about the probe and scan sequence have been added. (Not yet. Need to check with GE.)}
\\\\
In section “IV-A. Oversampling in transmit”: please confirm (specify) that 1x1 receive beamforming is performed at this point.
\textit{We have now specified that our starting point is a system with a one-to-one relationship between tx and rx beams.}
\\\\
In section “IV-B. Oversampling by parallel receive beamforming”, could you explain in more details what are the differences between Capon + STB and the technique proposed by Rabinovitch (2013) – reference [27]?
\textit{There are no differences. Rabinovitch (2013 (reference [25]) does not propose any new technique, it is just Capon + STB.}
\\\\
Page10 Column1 line56  write “should be removed” instead of “should be remove”
\textit{Misspelling has been corrected.}
\\\\
Page 10 Column 1 lines 40-60, you state that with synthetic transmit beamforming, some of the artifacts seen in oversampling in receive by phase rotation could be eliminated. It would be interesting to see such technique implemented.
\textit{It would, but while minimizing the length of the manuscript an actual result was left out. It should, however, be clear from how STB corrects errors introduced by PRB, that something similar will work for phase-rotated rx-beams.}
\\\\
P10 column 2 line 28-29 write “too extreme” instead of “to extreme”
\textit{Misspelling has been corrected.}
\\\\
Fig 6a: specify which beamforming is applied here (I suspect delay and sum with no multiline receive?). Maybe you want to consider showing still images of Capon and Capon-oversampled as well (not necessarily on fig. 6), just in case some people won’t look at the videos.
\textit{We have now specified that the image is processed with delay-and-sum beamformer. Default values for $p$ and $q$ are used and are therefore not specified. (Should we add images?)}
\end{document}

### 2014-02-18 HRUIofMovingObjects/jrnl_article.tex
Response to reviewers.

\subsection{Oversampling on Transmit}
A straight forward way of obtaining sufficient sampling in an active imaging system is by increasing the number of transmit beams (tx-beams) until the system is locally laterally shift-invariant. In Fig.\,\ref{fig:capon_oversampling_a} and Fig.\,\ref{fig:capon_oversampling_b} we have increased the tx-beam density by a $q$-factor of four and sixteen respectively. As expected the geometric distortion and scalloping loss decreases with increased lateral sampling. Note that Fig.\,\ref{fig:capon_oversampling_b} is zoomed compared to Fig.\,\ref{fig:capon} in order to better see the beam-to-beam variation.

@@

\begin{figure*}[!t]
\centerline{
\begin{tabular}{cc}
\subfloat[]{\includegraphics[width=0.5\linewidth]{\img fig6a.eps}\label{fig:image_das}}
\subfloat[]{\includegraphics[width=0.5\linewidth]{\img fig6b.eps}\label{fig:phantom_das}}\\
\subfloat[]{\includegraphics[width=0.5\linewidth]{\img fig6c.eps}\label{fig:phantom_capon_LSV}}
\subfloat[]{\includegraphics[width=0.5\linewidth]{\img fig6d.eps}\label{fig:phantom_capon_LSV_10PR}}
\end{tabular}
}
\caption{LSV-plots generated from \textit{in-vitro} phantom data where the probe has been manually dragged across the phantom. See the supplementary material for videos of the whole loop processed with the different beamformers \multimedia{Videos}. Capon beamforming has been performed with the same settings as in Fig.\,\ref{fig:capon1}. P-MAE is not shown due to a lack of probe movement control. a) First frame in the recorded loop. A white box indicates the point scatterer used to construct the LSV-plots.  b) Delay-and-sum beamforming. c) Capon beamforming without oversampling. d) Capon with ten times oversampling using phase rotation.}
\label{fig:LSV_invitro}
\end{figure*}

@@

Oversampling by phase rotation can therefore introduce similar block artifacts as parallel receive beamforming (PRB). These artifacts should be possible to remove in the same way as for PRB by using the synthetic transmit beamforming (STB) technique. If we distribute our steering angles in an overlapping scheme [like rx-beams are spread out for STB] we get a phase rotation version of STB where e.g. eight phase rotated beams are averaged into four. The geometric distortion, or stripes, seen at the bottom of the sector in the video with sixteen times oversampling \multimedia{Media Movie 3} should be remove by such technique.

When oversampling is applied it becomes evident that the high resolution settings used in this paper might be to extreme, both with respect to the level of required oversampling and the point scatterer's appearance. Traditionally in medical ultrasound imaging the point spread function is always wider laterally than in range. With the Capon beamformer this is now changed. A more symmetric point spread function while preserving speckle statistics is obtained with the parameters $L=M/4$ and $K=0$ \cite{Synnevag2007a}. The level of required oversampling and the computational complexity are also reduced. %Another option is to perform pulse inversion if a spiky symmetric point spread function is desirable.

>>>>

\subsection{Oversampling on Transmit}
A straight forward way of obtaining sufficient sampling in an active imaging system with an equal number of transmit (tx) and receive (rx) beams is to increasing the number of tx-beams until the system is locally laterally shift-invariant. In Fig.\,\ref{fig:capon_oversampling_a} and Fig.\,\ref{fig:capon_oversampling_b} we have increased the tx-beam density by a $q$-factor of four and sixteen respectively. As expected the geometric distortion and scalloping loss decreases with increased lateral sampling. Note that Fig.\,\ref{fig:capon_oversampling_b} is zoomed compared to Fig.\,\ref{fig:capon} in order to better see the beam-to-beam variation.

@@

\begin{figure*}[!t]
\centerline{
\begin{tabular}{cc}
\subfloat[]{\includegraphics[width=0.5\linewidth]{\img fig6a.eps}\label{fig:image_das}}
\subfloat[]{\includegraphics[width=0.5\linewidth]{\img fig6b.eps}\label{fig:phantom_das}}\\
\subfloat[]{\includegraphics[width=0.5\linewidth]{\img fig6c.eps}\label{fig:phantom_capon_LSV}}
\subfloat[]{\includegraphics[width=0.5\linewidth]{\img fig6d.eps}\label{fig:phantom_capon_LSV_10PR}}
\end{tabular}
}
\caption{LSV-plots generated from \textit{in-vitro} phantom data where the probe has been manually dragged across the phantom. See the supplementary material for videos of the whole loop processed with the different beamformers \multimedia{Videos}. Capon beamforming has been performed with the same settings as in Fig.\,\ref{fig:capon1}. P-MAE is not shown due to a lack of probe movement control. a) First frame in the recorded loop processed with delay-and-sum beamforming. A white box indicates the point scatterer used to construct the LSV-plots.  b) Delay-and-sum beamforming. c) Capon beamforming without oversampling. d) Capon with sixteen times oversampling using phase rotation.}
\label{fig:LSV_invitro}
\end{figure*}

@@

Oversampling by phase rotation can therefore introduce similar block artifacts as parallel receive beamforming (PRB). These artifacts should be possible to remove in the same way as for PRB by using the synthetic transmit beamforming (STB) technique. If we distribute our steering angles in an overlapping scheme [like rx-beams are spread out for STB] we get a phase rotation version of STB where e.g. eight phase rotated beams are averaged into four. The geometric distortion, or stripes, seen at the bottom of the sector in the video with sixteen times oversampling \multimedia{Media Movie 3} should be removed by such technique.

When oversampling is applied it becomes evident that the high resolution settings used in this paper might be too extreme, both with respect to the level of required oversampling and the point scatterer's appearance. Traditionally in medical ultrasound imaging the point spread function is always wider laterally than in range. With the Capon beamformer this is now changed. A more symmetric point spread function while preserving speckle statistics is obtained with the parameters $L=M/4$ and $K=0$ \cite{Synnevag2007a}. The level of required oversampling and the computational complexity are also reduced. %Another option is to perform pulse inversion if a spiky symmetric point spread function is desirable.
